---
title: "Final Project 2: R Markdown"
author: "Amina Kadric"
date: "2024-10-07"
output: html_document
echo: false
---

# Introduction

The data include is statistics and information on the Atlanta Braves' batters between 1966 and 2023. Some of the statistics include the players' age, number of hits in a season, and number of balls hit. I plan to do a descriptive comparative analysis between years 1995 and 2021 which are the two times when the Braves won the World Series. 


``` {r, import-data, echo = FALSE}
here::i_am("Final_Project2_AK.Rmd")
absolute_file_to_data <- here::here("data", "ATL_batting.csv")
data1 <- read.csv(absolute_file_to_data, header = TRUE)
```



```{r, data-cleaning}

```

#Table 

This table includes the mean, standard deviation, median, and number of observation for batting stats for 1999 and 2021

```{r, data-tables}

```


# Graph

The graph below shows the relationship between the number of games played and players' batting average.

```{r, data-graph}
library(ggplot2)

data2 |>
  group_by(games) |>
ggplot(aes(x = games, y = batting_average)) +
  geom_point(aes(color = year))
```


