---
title: "Final Project: Atlanta Braves World Series Stats - 1995 and 2021"
author: "Amina Kadric"
date: "`r Sys.Date()`"
output: 
  html_document:
  toc: TRUE
---

```{r, packages, echo=FALSE}
library(knitr)
```

# Introduction

The data include is statistics and information on the Atlanta Braves' batters between 1966 and 2023. Some of the statistics include the players' age, number of hits in a season, and number of balls hit. This report aims to compare players' stats between the 1995 and 2021
which are the two years the Atlanta Braves won the World Series.


```{r, report-location, include=FALSE}
here::i_am("Final_Project2_AK.Rmd")
```


```{r, data-cleaning, include=FALSE}
here::i_am("Final_Project2_AK.Rmd")

clean_data <- readRDS(
  file = here::here("output/cleaned_batting_no_pitchers.rds")
)

```


# Tablular Analysis

This table includes the mean, standard deviation, median, and number of observation for batting stats for 1995 and 2021.

```{r, data-tables, echo = FALSE}
descriptive_table <- readRDS(
  file = here::here("output/descriptive_table.rds")
)

descriptive_table
```


# Box Plot

The figure below represents the distribution of player's batting average between 1995 and 2021. The box plots for each year is stratified between dominant hand.

```{r, boxplot_batting_average, echo=FALSE}

#| fig.align = "center",
#| out.width = "700px"

knitr::include_graphics(
  here::here("output/box_plot.png")
)
```


